Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-06-11 paper/paper.tex
Plotting

\section{Parallel Search}

\section{Experiments}

>>>>

\section{Experiments with Parallel Search}

?? Hardware.

?? Datasets.

\subsection{Parallel Search is Better Overall}

\begin{figure}[p]
    \includegraphics*{gen-graph-cumulative-plain.pdf}
    \hfill
    \includegraphics*{gen-graph-cumulative-33v.pdf}

    \vspace*{1em}

    \includegraphics*{gen-graph-cumulative-33ved.pdf}
    \hfill

\end{figure}

\begin{figure}[p]
    \includegraphics*{gen-graph-scatter-plain-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-clique-vs-clique-cilk-t32.pdf}

    \vspace*{1em}

    \includegraphics*{gen-graph-scatter-plain-kdown-vs-kdown-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-kdown-vs-kdown-cilk-t32.pdf}

    \vspace*{1em}

    \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t32.pdf}

\end{figure}

\begin{figure}[p]
    \includegraphics*{gen-graph-scatter-plain-clique-par-t32r-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-clique-cilk-t32r-vs-clique-cilk-t32.pdf}

    \vspace*{1em}

    \includegraphics*{gen-graph-scatter-plain-kdown-par-t32r-vs-kdown-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-kdown-cilk-t32r-vs-kdown-cilk-t32.pdf}

    \vspace*{1em}

    \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t32r-vs-mcsplit-par-t32.pdf}

\end{figure}

\begin{figure}[p]
    \includegraphics*{gen-graph-scatter-33v-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33v-clique-vs-clique-cilk-t32.pdf}

    \vspace*{1em}

    \includegraphics*{gen-graph-scatter-33v-mcsplit-vs-mcsplit-par-t32.pdf}
\end{figure}

\begin{figure}[p]
    \includegraphics*{gen-graph-scatter-33v-clique-par-t32r-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33v-clique-cilk-t32r-vs-clique-cilk-t32.pdf}

    \vspace*{1em}

    \includegraphics*{gen-graph-scatter-33v-mcsplit-par-t32r-vs-mcsplit-par-t32.pdf}

\end{figure}

\begin{figure}[p]
    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-cilk-t32.pdf}

    \vspace*{1em}

    \includegraphics*{gen-graph-scatter-33ved-mcsplit-vs-mcsplit-par-t32.pdf}
\end{figure}

\begin{figure}[p]
    \includegraphics*{gen-graph-scatter-33ved-clique-par-t32r-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t32r-vs-clique-cilk-t32.pdf}

    \vspace*{1em}

    \includegraphics*{gen-graph-scatter-33ved-mcsplit-par-t32r-vs-mcsplit-par-t32.pdf}

\end{figure}
